Tulai

### 2023-09-16 paper/paper_tulai.qmd
update on n_distinct with na.rm

# Convert each column to numeric
for (col_name in columns_to_convert) {
  # Replace non-numeric characters with NA
  tl_final[[col_name]][tl_final[[col_name]] %in% c("", "NA", "N/A")] <- NA
  # Convert to numeric
  tl_final[[col_name]] <- as.numeric(tl_final[[col_name]])
}

@@

```{r}
# Generate a summary table by grouping by 'depth'
summary_table_depth_tool_type <- tl_final %>%
  group_by(depth) %>%
  summarise(tool_type = n_distinct(tooltypegroup))

>>>>

# Convert each column to numeric
for (col_name in columns_to_convert) {
  # Replace non-numeric characters with NA
  # BM: this is quite an unusual method for doing this, 
  # where did you find it?
  tl_final[[col_name]][tl_final[[col_name]] %in% c("", "NA", "N/A")] <- NA
  # Convert to numeric
  tl_final[[col_name]] <- as.numeric(tl_final[[col_name]])
}

# BM: this is how I would convert those columns to numeric, 
# I think it's easier to read and requires less typing
# tl_final %>% 
#  mutate(across(all_of(columns_to_convert), parse_number))

@@

```{r}
# Generate a summary table by grouping by 'depth'
summary_table_depth_tool_type <- tl_final %>%
  group_by(depth) %>%
  summarise(tool_type = n_distinct(tooltypegroup, na.rm = TRUE))
